% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Xiao-yu Wang}

\basicInfo{
  \email{xiao-yuwang@outlook.com} \textperiodcentered\ 
  \phone{(+86) 182-7377-0670} \textperiodcentered\ 
  \linkedin[XIAO-YU WANG]{https://www.linkedin.com/in/xiao-yu-wang-13a345330}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Tongji University (Tongji)}, Shanghai, China}{2022 -- Present}
\textit{B.S.} in Computer Science (CS), expected July 2026
\begin{itemize}
  \item GPA: 88.91/100
  \item Major Courses: Advanced Programming, Database Systems, Data Structures, AI (all 5.0/5.0)
\end{itemize}

\section{\faUsers\ Experience}

\datedsubsection{\textbf{NIO Inc. (a leading New Energy Vehicle manufacturer)}}{Mar. 2025 -- Jul. 2025}
\role{Algorithm Development Intern}{Manager: Ugur Ersoy}
\begin{itemize}
  \item Engineered an intelligent defect warning system for stamping production lines using a fine-tuned YOLOv11-seg model for image segmentation and detection. Achieved a precision of 97.34\% and a recall of 89.60\%, significantly enhancing quality control efficiency.
  \item Architected an end-to-end pipeline from data acquisition and preprocessing to model inference and real-time alerting. Deployed the system across two production lines, achieving a monthly alert accuracy rate of over 92\% via a Feishu (Lark) bot.
  \item Developed a Multi-Agent collaborative system utilizing function calling to interact with Feishu APIs for real-time Personal Protective Equipment (PPE) violation detection. Implemented an automated notification mechanism, including meeting requests and alerts to responsible personnel.
  \item Developed a custom component for an internal AI workflow orchestration platform, enabling users to seamlessly retrieve and integrate content from Feishu (Lark) documents directly into their AI workflows.
\end{itemize}

\datedsubsection{\textbf{Helmholtz Centre for Infection Research (HZI)} Germany (Remote)}{Dec. 2023 -- Present}
\role{Research Assistant}{Supervisor: Prof. Till Strowig \& Dr. Kun D. Huang}
\begin{itemize}
  \item Co-authored a manuscript currently under review at \textit{Cell Reports Medicine} (Impact Factor: 10.6), based on a Random Forest analysis of microbial data from 400+ bacteria and 190+ patient samples that achieved 76.93\% accuracy.
  \item Spearheaded the development of \textbf{MetaDock} as \textbf{first author}, a browser-accessible platform designed to deploy complex bioinformatics tools on High-Performance Computing (HPC) clusters for researchers without programming expertise.
  \item Engineered key technical features for MetaDock, including the automatic generation of web GUIs from command-line tools and the integration of a \textbf{built-in AI assistant} to provide users with instant, expert advice on tools and workflows.
  \item Authored the first-author abstract for this work, which was accepted for a poster presentation at the prestigious \textit{EMBO | EMBL Symposium: The Human Microbiome} (Sep. 2025).
\end{itemize}

%\datedsubsection{\textbf{Elderly and Funeral Service Management Platform Design}}{May. 2024 -- Nov. 2024}
%\role{Database Developer and Web Designer}{Individual Projects}
%Overview: Designed and implemented a database system for elderly and funeral services.
%\begin{itemize}
%  \item Developed a relational database for 400+ elderly care institutions and 100+ funeral service providers.  
%  \item Integrated service ratings and feedback to optimize institutional management.
%  \item Used MySQL, Python, Flask, HTML, CSS, JavaScript for full-stack implementation.
%\end{itemize}

%\datedsubsection{\textbf{Mathematical Contest In Modeling(APMCM)}}{Oct. 2023 -- Jan. 2024}
%\role{Team Leader}{Competition Project}
%Overview: Led a team in a computer vision task for apple variety classification. 
%\begin{itemize}
% \item Led a team of 3 to develop a fruit image recognition system for apple detection, ripeness estimation, and differentiation, trained on 10,000+ images with 90\% accuracy using YOLO and RESNET models.  
%  \item Enhanced team communication, completing the project 12 hours ahead of the 3-day deadline.
%\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C, C++, Python
  \item Platforms: Windows, Linux, MacOS
  \item Development: Frontend (HTML/CSS, JavaScript); Backend (Node.js, Flask); Database (MySQL)
  \item Tools \& Frameworks: Git, Docker, PyTorch
  \item Computer Science Fundamentals: Operating Systems, Databases, Algorithms, Computer Networks
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{3} Prize}, Award on Outstanding Undergraduate Student Scholarship, Tongji University}{Dec. 2023}
\datedline{\textit{\nth{3} Prize}, Award on APMCM (Asia-Pacific Mathematical Contest in Modeling) }{Jan. 2024}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: https://github.com/hoshigawarei
  \item Languages: English - Fluent (TOEFL: 104, Speaking: 27), Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
